### 2019-08-09 EJSSubmission/WeightedSign_EJS_Introduction_02_24_19_1.tex
EJS revision commit 080919

\rework{
There are two unknown quantities in the generalized sign function as defined in \eqref{eq:GSign}: $\mu$ and $\BF$, To estimate dispersion and its eigen-structure robustly, we must start with a robust estimator for $\mu$. In Section~\ref{Sec:WSQuantiles} we present the case for \textit{weighted spatial quantiles}, which can be defined and studied in very general spaces 
$\cX$. One special case of this is the {\it weighted spatial median}. As a location estimator, it has several interesting robustness properties and can be shown to be more efficient that some existing robust location estimators, thus making it a perfect candidate to estimate $\mu$. On the other hand, setting $\BF$ as $\BF_X$, i.e. the distribution of $X$ has the clear interpretation of differentially weighting observations based on their inlyingness to the overall data distribution. This mirrors the context of how data depth has been used in the literature (refs). Due to this reason, except for two results in Section~\ref{Sec:WSQuantiles} (Theorem~\ref{Thm:WSMedian} and Corollary~\ref{Cor:ARE}) we assume $\BF \equiv \BF_X$ for the rest of the paper. However, other choices of $\BF$ may lead to interesting interpretations of $W(. ,\BF)$ and the resulting quantities, e.g. (ref), and can potentially be explored further.
}

>>>>

\rework{
There are two unknown quantities in the generalized sign function as defined in \eqref{eq:GSign}: $\mu$ and $\BF$, To estimate dispersion and its eigen-structure robustly, we must start with a robust estimator for $\mu$. In Section~\ref{Sec:WSQuantiles} we present the case for \textit{weighted spatial quantiles}, which can be defined and studied in very general spaces 
$\cX$. One special case of this is the {\it weighted spatial median}. As a location estimator, it has several interesting robustness properties and can be shown to be more efficient that some existing robust location estimators, thus making it a perfect candidate to estimate $\mu$. On the other hand, setting $\BF$ as $\BF_X$, i.e. the distribution of $X$ has the clear interpretation of differentially weighting observations based on their inlyingness to the overall data distribution. This mirrors the context of how data depth has been used in the literature (refs). Due to this reason, except for the first result in Section~\ref{Sec:WSQuantiles} (Theorem~\ref{Thm:WSMedian}) we assume $\BF \equiv \BF_X$ for the rest of the paper. However, other choices of $\BF$ may lead to interesting interpretations of $W(. ,\BF)$ and the resulting quantities, e.g. (ref), and can potentially be explored further.
}

### 2019-08-09 EJSSubmission/WeightedSign_EJS_WeightedSpatialQuantiles_02_24_19_1.tex
EJS revision commit 080919

Suppose the open unit sphere in $\cX$ is given by 
$\textrm{int} {\cX}_{0; 1} = \{ x \in \cX: | x | < 1 \}$, and let
 $u \in \textrm{int} {\cX}_{0; 1}$. We also fix the set of probability measures $\cM$, 
 and select $\BF \in \cM$. Consider a random element $X \in \cX$. 
We define the $(u, \BF)$-th \textit{weighted spatial quantile} of $\cX$ 
as the minimizer $q (u, \BF) \in \cX$ of 
\baq
\Psi (q; u, \BF) = \BE \Bigl[ W (X, \BF) \bigl\{ | X - q | 
+ \langle u, X - q \rangle \bigr\} \Bigr].
\label{eq:WeightedQuantile}
\eaq
%
\rework{
This is a natural generalization of the spatial median \cite{ref:JASA96862_Chaudhuri, ref:Biometrika48414_Haldane,ref:AoS97435_Koltchinskii}, or more general spatial quantiles \cite{ref:AoS17591_Cardotetal_Median_HilbertSpace, ref:AoS141203_ChakrabortyChaudhuri_Banach_Quantile, ref:Bernoulli152308_Minsker_Median_Banach}. In what follows, for brevity we elaborate only the case of the \textit{weighted spatial median} (thus 
$\Psi (q; 0, \BF) = \BE \bigl[ W (X, \BF) | X - q | \bigr] $) for the case of finite dimensional $\cX$. Specifically, we demonstrate the utility of using the {\it weighted} spatial median as opposed to using the traditional, unweighted versions found in literature. The analysis and computation of the general weighted spatial quantiles will largely follow by extending the results of the above cited references, and we postpone details to a future study.
}

Assume that we have independent and identically distributed observations $X_{1}, \ldots, X_{n} \in \cX$, and the sample weighted spatial median is computed by minimizing $\Psi_{n} (q; 0, \BF) = \sum_{i = 1}^{n} \bigl[ W (X_{i}, \BF) | X_{i} - q | \bigr] $, and is denoted by $\hat{q}_{nW}$, the second subscript is in acknowledgement that the weight function is used. We denote the unweighted version of this estimator, ie, the case where $W (X, \BF) \equiv 1$ as $\hat{q}_{n}$. Assume the following technical conditions:

@@

 \begin{Theorem}
 \label{Thm:WSMedian}
 Under assumptions \textbf{[A1] - [A3]}, we have 
 \ban 
 n^{1/2} (\hat{q}_{nW} - q_{0}) & \draro N(0, \Psi_{2}^{-1} \Psi_{1}^{2} \Psi_{2}^{-1}), 
 \text{ where } \\
 \Psi_{2} & = 
 \BE W (X, \BF) \Bigl[  |X - q|^{-1} \BI_{p} - |X - q|^{-3/2} (X - q) (X - q)^{T}  \Bigr] 
 \\
 \Psi_{1}  & = n \BE   W^{2} (X, \BF)  \bfS (X; q_{0}) \bfS^{T} (X; q_{0}).
 \ean
 \end{Theorem}
Thus, under very standard regularity conditions, the sample weighted spatial median 
is consistent and is asymptotically normal.  
Theorem~\ref{Thm:WSMedian}  can be proved in several different ways. We have used 
techniques following \cite{ref:AoS891631_Haberman, ref:AoS921514_Niemiro}, 
we omit the details.

@@

\begin{Corollary}
\label{Cor:ARE}
Assume that $|X - q_{0}|$ and $S (X; q_{0})$ are independent, and the weight function 
$W (X, \BF)$ is a function of  $|X - q_{0}|$. Then
\ban
& ARE (\hat{q}_{nW}, \hat{q}_{n}) \\
& = 
\Bigl[ \BE \bigg(  |X - q_{0}|^{-1} \bigg) \Bigr]^{-2}
\Bigl[ \BE W^{2} (X, \BF) \Bigr]^{-1}
\Bigl[ \BE \bigg(  |X - q_{0}|^{-1} W (X, \BF) \bigg) \Bigr]^{2}.
\ean
Consequently, if $W (X, \BF) = k   |X - q_{0}|^{-1}$ for some $k \in (0, 1]$, 
then this asymptotic relative efficiency is 
$ \{k^{-1} (\BE ||X - q_{0}|^{-1} )^{2} \BE |X - q_{0}|^{-2} \}^{1/p}> 1$. 
\end{Corollary}

@@

\begin{Corollary}
\label{Cor:Elliptic_ARE}
Assume that the tuning parameter of the weight function, $\BF$, is  the 
distribution of $X$, and is an elliptically symmetric distribution, and $\mu = q_{0}$. 
Also assume that the weight function is affine invariant, that is:
\ban
W (A x + b, A \BF + b) = W (x, \BF),
\ean
Then  the weight function satisfies $W (X, \BF) = W (Z, \BF_{Z})$, and 
hence may be further restricted to be a function of $|Z|$. Then 
$S (X; q_{0})$ is uniform on the unit ball 
in $\BR^{p}$, and is independent of $|X - q_{0}|$, while 
$W (X, \BF)$ is a function of  $|X - q_{0}|$. That is, the conditions of 
Corollary~\ref{Cor:ARE} are satisfied. 
\end{Corollary}

>>>>

Suppose the open unit sphere in $\cX$ is given by 
$\textrm{int} {\cX}_{0; 1} = \{ x \in \cX: | x | < 1 \}$, and let
 $u \in \textrm{int} {\cX}_{0; 1}$. We also fix the set of probability measures $\cM$, 
 and select $\BF \in \cM$. Consider a random element $X \in \cX$. 
We define the $(u, \BF)$-th \textit{weighted spatial quantile} of $\cX$ 
as the minimizer $q (u, \BF) \in \cX$ of 
\baq
\Psi (q; u, \BF) = \BE \Bigl[ W (X, \BF) \bigl\{ | X - q | 
+ \langle u, X - q \rangle \bigr\} \Bigr].
\label{eq:WeightedQuantile}
\eaq
%
%\rework{
\noindent
This is a natural generalization of the spatial median \cite{ref:JASA96862_Chaudhuri, ref:Biometrika48414_Haldane,ref:AoS97435_Koltchinskii} ($W(X, \BF) \equiv 1$ and $u = {\bf 0}_p$), or more general spatial quantiles \cite{ref:AoS17591_Cardotetal_Median_HilbertSpace, ref:AoS141203_ChakrabortyChaudhuri_Banach_Quantile, ref:Bernoulli152308_Minsker_Median_Banach} ($W(X, \BF) \equiv 1$).

In what follows, for brevity we elaborate only the case of the \textit{weighted spatial median} (thus $\Psi (q; 0, \BF) = \BE \bigl[ W (X, \BF) | X - q | \bigr] $) for the case of finite dimensional $\cX$. Specifically, we demonstrate the utility of using the {\it weighted} spatial median as opposed to using the traditional, unweighted versions found in literature. The analysis and computation of the general weighted spatial quantiles will largely follow by extending the results of the above cited references, and we postpone details to a future study.
%}

Assume that we have independent and identically distributed observations $X_{1}, \ldots, X_{n} \in \cX$, and the sample weighted spatial median is computed by minimizing $\Psi_{n} (q; 0, \BF) = \sum_{i = 1}^{n} W (X_{i}, \BF) | X_{i} - q | $, and is denoted by $\hat{q}_{nW}$, the second subscript is in acknowledgement that the weight function is used. We denote the unweighted version of this estimator, ie, the case where $W (X, \BF) \equiv 1$ as $\hat{q}_{n}$. Assume the following technical conditions:

@@

 \begin{Theorem}
 \label{Thm:WSMedian}
 Under assumptions [A1]-[A3], we have 
 \ban 
 n^{1/2} (\hat{q}_{nW} - q_{0}) & \draro N(0, \Psi_{2}^{-1} \Psi_{1}^{2} \Psi_{2}^{-1}), 
 \text{ where } \\
 \Psi_{2} & = 
 \BE W (X, \BF)\Bigl[  |X - q|^{-1} \BI_{p} - |X - q|^{-3/2} (X - q) (X - q)^{T}  \Bigr] 
 \\
 \Psi_{1}  & = \BE   W^{2} (X, \BF)  S (X; q_{0}) S^{T} (X; q_{0}).
 \ean
 \end{Theorem}

%\rework{
Thus, under very standard regularity conditions, the sample weighted spatial median 
is consistent and is asymptotically normal. Theorem~\ref{Thm:WSMedian}  can be proved in several different ways. Here we use techniques following \cite{ref:AoS891631_Haberman, ref:AoS921514_Niemiro}. Specifically, following Theorem 4 in \cite{ref:AoS921514_Niemiro}, which traces back to \cite{ref:AoS891631_Haberman} with slightly relaxed conditions, we get
%
\begin{align*}
n^{1/2} (\hat{q}_{nW} - q_{0}) =
- \frac{\Psi_2}{\sqrt n} \sum_{i=1}^n W (X_i, \BF)  S (X_i; q_0) + o_P(1).
\end{align*}
%
Theorem~\ref{Thm:WSMedian} follows by applying the central limit theorem.
%}

@@

\begin{Corollary}
\label{Cor:ARE}
\hl{Assume that the tuning parameter of the weight function, $\BF$}, is  the distribution of $X$. Also assume $|X - q_{0}|$ and $S (X; q_{0})$ are independent, and the weight function $W (X, \BF)$ is a function of  $|X - q_{0}|$. Then
\ban
& ARE (\hat{q}_{nW}, \hat{q}_{n}) \\
& = 
\Bigl[ \BE \bigg(  |X - q_{0}|^{-1} \bigg) \Bigr]^{-2}
\Bigl[ \BE W^{2} (X, \BF) \Bigr]^{-1}
\Bigl[ \BE \bigg(  |X - q_{0}|^{-1} W (X, \BF) \bigg) \Bigr]^{2}.
\ean
Consequently, if $W (X, \BF) = k   |X - q_{0}|^{-1}$ for some $k \in (0, 1]$, 
then this asymptotic relative efficiency is 
$ \{k^{-1} (\BE |X - q_{0}|^{-1} )^{2} \BE |X - q_{0}|^{-2} \}^{1/p}> 1$. 
\end{Corollary}

@@

\begin{Corollary}
\label{Cor:Elliptic_ARE}
Assume that $\BF \equiv \BF_X$ is an elliptically symmetric distribution, and $\mu = q_{0}$. 
Also assume that the weight function is affine invariant, that is:
\ban
W (A x + b, A \BF + b) = W (x, \BF),
\ean
Then  the weight function satisfies $W (X, \BF) = W (Z, \BF_{Z})$, and 
hence may be further restricted to be a function of $|Z|$. Then 
$S (X; q_{0})$ is uniform on the unit ball 
in $\BR^{p}$, and is independent of $|X - q_{0}|$, while 
$W (X, \BF)$ is a function of  $|X - q_{0}|$. That is, the conditions of 
Corollary~\ref{Cor:ARE} are satisfied. 
\end{Corollary}
